% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009 
\documentclass{acm_proc_article-sp}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
%\usepackage{soul}

\usepackage{float}

\floatstyle{ruled}
\newfloat{program}{thp}{lop}
\floatname{program}{Program}

\begin{document}

\title{Multipipes: Exploring Disjuntive Classifications in Hyperpipes}
\subtitle{[In an exciting manner]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}

\numberofauthors{2} 
%
\author{
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Aaron Riesbeck\\
       \affaddr{West Virginia University}\\
       \affaddr{100 Address Lane}\\
       \affaddr{Morgantown, WV 26505}\\
       \email{ariesbeck@theriac.org}
% 2nd. author
\alignauthor
Adam Brady\\
       \affaddr{West Virginia University}\\
       \affaddr{100 Fake St.}\\
       \affaddr{Morgantown, WV 26505}\\
       \email{adam.m.brady@gmail.com}
}
\date{12 October 2009}

\maketitle
\begin{abstract}

This paper explores classifiction with disjunctive sets using a modified form of HyperPipes~\cite{Eisenstein04} called MultiPipes. Rather than apply HyperPipes it's intended sparse datasets, we find that it's application to non-sparse, many-class datasets typically results in several tied classification scores which we then union into a disjunction. This union presents interesting possibilities in it's high accuracy in containing the target class. Although we initially cannot predict single classes, we find that these disjunctions often eliminate large portions of possible classes. Essentialy we aren't certain what the class is, but we are very certain of what the class is not. The rest of the paper explores two alternative strategies with MultiPipes. The first involves methods of reducing the disjunctive sets to single classifications. The second considers growing the disjunctive sets to optimize the accuracy of containment vs. set size.

\end{abstract}

\keywords{HyperPipes, disjoint sets, \LaTeX, multiple classes, indecisive learners} % NOT required for Proceedings


\section{Introduction to HyperPipes}

\input{sections/an-introduction.tex}

\subsection{Pseudocode for hyperpipes}

\input{sections/pseudocode.tex}

\subsection{The Problem with HyperPipes}

\input{sections/hyperpipes-problem.tex}

\subsection{Patching HyperPipes}

\input{sections/fixing-hyperpipes.tex}

\section{Narrowing vs. Classifying}

\input{sections/why-multipipes.tex}

\section{Preliminary Results}

Description of results
\begin{itemize}
	\item{incremental learning}
	\item{batch learning}
	\item{weighted distance}
	\item{centroids via overlap}
	\item{increasing alpha}
\end{itemize}

\subsection{Disjoint Learning}

\input{sections/results-disjoint.tex}

\subsection{Breaking the Ties}

\input{sections/results-weighted-distance.tex}

\input{sections/results-centroid.tex}

\subsection{Casting a wider net}

\input{sections/results-alpha.tex}

\section{Preliminary Conclusions}

\input{sections/conclusion.tex}

% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{multipipes}  %the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references

\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
%\thebibliography{}
\balancecolumns
\end{document}
